### 2011-03-16 code/subarchitectures/vision.sa/branches/post-review-yr2-11533/src/c++/vision/components/VisualLearner/test/gy2report/gy2article.tex
gy2 test report update

@@

We have 1200 image pairs in the database. Some (less than 10) of the image
pairs cause the components {\em PlanePopout} or {\em SOIFilter} to crash. In
average we can run the system for about 100 objects before we have to restart
it.

We also made an interesting observation in the {\em stWaitForLearningTask}
state. This state is reached $2$ times while the object is on the scene. After
the tutor describes the shape, the first learning task is created after $3-5$
seconds. When the learning is complete the tutor then waits for $2s$ and
describes the color of the object.  The interesting thing about the second
LearningTask task is that it's time to appear increases with the system's
running time. Initially it is the same as for the first LearningTask. After
$4000s$ it increases to $7s$ and after $7000s$ it takes $12s$ for it to appear.
Finally the system stops resonding as described above.

>>>>

When the state machine comes into the state {\em stObjectOn} we wait for $5s$
so that the scene can become stable. Sometimes more than one VisualObject is
created for a presented object. In some other cases the object is not well
defined and can disappear. We want to make sure the scene is stable before we
prevent the changes of the set of VisualObjects in the WM.

In the state {\em stUnloadScene} the system waits for another $5s$ before it
replaces the scene with an empty one. Without this timeout, the planner would
lock again.

@@

We also made an interesting observation in the {\em stWaitForLearningTask}
state. This state is reached $2$ times while the object is on the scene. After
the tutor describes the shape, the first learning task is created after $3-5$
seconds. When the learning is complete the tutor then waits for $2s$ and
describes the color of the object.  The interesting thing about the second
LearningTask task is that it's time to appear increases with the system's
running time. Initially it is the same as for the first LearningTask. After
$4000s$ it increases to $7s$ and after $7000s$ it takes $12s$ for it to appear.
Finally the system stops resonding as described above.  The increasing time
could be related to the increasing number of messages from the planner:
``Pointer to belief xxx cannot be resolved''.

\subsection{Other crashes}

The c++ server sometimes crashes right after the message ``Planner has
attempted to overwrite an outdated WM entry. WMA:
XX:goal.scheduler:data:planner.sa.  Local version: 5.  WM version: 6''.

Some of the image pairs (less than 10 out of $1200$ in the database) cause the
components {\em PlanePopout} or {\em SOIFilter} to crash.
